Exploring the Design Space of Differentially Private Bayesian Inference under Hellinger Distance

### 2020-05-11 ICML2019/main.tex
updates

\noindent \emph{Laplace mechanism.}
The Laplace mechanism releases a random number drawn from the Laplace distribution with
mean $\mu=q(d)$ and scale $\nu$. Where $q$ is a numeric query on a database $d$.
If $\nu\geq \frac{\Delta_f}{\epsilon}$, with $\Delta_f=\displaystyle\max_{d,d':\adj{d}{d'}}{\lvert f(d_1)-f(d_2)\lvert}$
then the mechanism is $\epsilon$-differentially private as proven in \cite{???}.

>>>>

\noindent \emph{Laplace mechanism.}
The Laplace mechanism releases a random number drawn from the Laplace distribution with
mean $\mu=q(d)$ and scale $\nu$. Where $q$ is a numeric query on a database $d$.
If $\nu\geq \frac{\Delta_f}{\epsilon}$, with $\Delta_f=\displaystyle\max_{d,d':\adj{d}{d'}}{\lvert f(d_1)-f(d_2)\lvert}$
then the mechanism is $\epsilon$-differentially private as proven in \cite{Zhang2017privbayes}
